### 2025-01-17 index.qmd
20250108 - minor edits
20250117 - 2025 citation

Petersen, I. T. (2024). *Fantasy football analytics: Statistics, prediction, and empiricism Using R*. Version 0.0.1. University of Iowa Libraries. <https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook>. [INSERT DOI LINK]

@@

```{bibtex}
@book{petersenFantasyFootballAnalytics,
  title = {Fantasy football analytics: Statistics, prediction, and empiricism using {R}},
  author = {Petersen, Isaac T.},
  year = {2024},
  publisher = {{University of Iowa Libraries}},
  note = {Version 0.0.1},
  doi = {INSERT},
  isbn = {INSERT},
  url = {https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook}
}
```

>>>>

Petersen, I. T. (2025). *Fantasy football analytics: Statistics, prediction, and empiricism using R*. Version 0.0.1. University of Iowa Libraries. <https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook>. [INSERT DOI LINK]

@@

```{bibtex}
@book{petersenFantasyFootballAnalytics,
  title = {Fantasy football analytics: Statistics, prediction, and empiricism using {R}},
  author = {Petersen, Isaac T.},
  year = {2025},
  publisher = {{University of Iowa Libraries}},
  note = {Version 0.0.1},
  doi = {INSERT},
  isbn = {INSERT},
  url = {https://github.com/isaactpetersen/Fantasy-Football-Analytics-Textbook}
}
```
